Temporal stability in human interaction networks

### 2015-06-30 paper.tex
adicionadas paginas incorporadas e anotadas da revisao do ricardo

\begin{table}
	\caption{Activity in the days along the month for MET list. Nearly identical distributions are found on other lists as indicated in Section~\ref{si:monthdays} of the Supporting Information. Although slightly higher activity rates are found in the beginning of the month, the most important feature seems to be the homogeneity made explicit by the high circular dispersion in Table~\ref{tab:circ}.}
	\footnotesize
	\input{tables/tabMonthdaysMET}
	\label{tab:min}
\end{table}

@@

The distribution of vertices in the hubs, intermediary, periphery Erd\"os sectors is remarkably stable along time, provided that a sufficiently large sample of 200 or more messages is considered. 
Moreover, the same distribution applies to the networks of all email lists analyzed, as demonstrated in Figure~\ref{fig:sectIL} and in Section~\ref{si:frac} of the Supporting Information. 
Activity is highly concentrated on the hubs, while a very large number of peripheral vertices contribute to only a fraction of the activity. This is expected for a system with a scale-free trace, as confirmed with the data in Table~\ref{autores} for the distribution of activity among participants.

>>>>

\begin{table}
	\caption{Activity in the days along the month for the MET list. Nearly identical distributions are found on other lists as indicated in Section~\ref{si:monthdays} of the Supporting Information. Although slightly higher activity rates are found in the beginning of the month, the most important feature seems to be the homogeneity made explicit by the high circular dispersion in Table~\ref{tab:circ}.}
	\footnotesize
	\input{tables/tabMonthdaysMET}
	\label{tab:min}
\end{table}

@@

The distribution of vertices in the hubs, intermediary, periphery Erd\"os sectors is remarkably stable along time, provided that a sufficiently large sample of 200 or more messages is considered. 
Moreover, the same distribution applies to the networks of all email lists analyzed, as demonstrated in Figure~\ref{fig:sectIL} and in Section~\ref{si:frac} of the Supporting Information. 
Activity is highly concentrated on the hubs, while a very large number of peripheral vertices contribute to only a fraction of the activity. This is expected for a system with a scale-free profile, as confirmed with the data in Table~\ref{autores} for the distribution of activity among participants.
